Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
remove the description of the controllers

Two proportional-integral (PI) controllers are designed by Wang {\it et al.} 
for the cruise control plant $G(z)$~\cite{DBLP:conf/hybrid/WangGRJF16}, 
which has the following mathematical model
%
\begin{equation}
\label{cruise-control-g1}
C_{1}(z)=\frac{1.51z-1.3586}{z-1}, \nonumber
\end{equation} 
%
\begin{equation}
\label{cruise-control-g2}
C_{2}(z)=\frac{2.72z^2 - 4.153z + 1.896}{1.0z^2 - 1.844z + 0.8496}. \nonumber
\end{equation}

The second set of benchmarks considers a simple spring-mass 
damper~\cite{DBLP:conf/hybrid/WangGRJF16}, where both discrete 
plant dynamics and controller are represented by the following 
z-expression, resp.
%
\begin{equation}
\label{spring-mass-damper-g}
G_2(z)=\frac{5\times{10^{-5}}z + 5\times{10^{-5}}}{z^2 - 2z + 1.0001}, \nonumber
\end{equation} 
%
\begin{equation}
\label{spring-mass-damper-c}
C_3(z)=\frac{1.28\times{10^{3}}z^2 - 1.354240\times{10^{3}}z + 0.074879\times{10^{3}}}{z^2 - 1.4990z + 0.4995}. \nonumber
\end{equation}

A third set of benchmarks that consists of digital controllers for satellite
applications is considered~\cite{Franklin15}, in order to evaluate the
present approach full capabilities.  In particular, satellites often require
attitude (pose) control for proper orientation of antennas and sensors
w.r.t.  earth.  The satellite attitude control is typically used for
three-axis attitude tracking, but here only one axis at a time is
considered.  The motion equation for the one-axis system, despising
disturbance torques, is given by:
%
\begin{equation}
\label{eq:satelliteode}
I\cdot \ddot{\theta} = \tau_{C},
\end{equation}

\noindent where $I$ is the inertia moment of satellite about its mass center, $\tau_{C}$ is the control 
torque applied by thusters, and $\theta$ is the controlled attitude angle. 
Normalizing Eq.~\eqref{eq:satelliteode} by defining the control signal $u=\frac{\tau_{C}}{I}$ and 
taking Laplace transform, the following $s$-domain transfer function $G(s)$ is obtained:
%
\begin{equation}
\label{eq:satellitetf}
G_{3}(s)=\frac{\theta(s)}{u(s)}=\frac{1}{s^2},
\end{equation}

\noindent using the ZOH discretisation defined in Eq.~\eqref{eq:pulsetf}, 
the following $z$-domain model is obtained:
\begin{equation}
G_{3}(z)= \frac{T^{2}}{2} \frac{z+1}{(z+1)^{2}}.
\end{equation}

The discrete controllers $C_{4}$ and $C_{5}$ for the satellite plant $G_{3}$, discretized with sample time $1s$ and $2s$ respectively, 
are represented by the following z-expression:
%
\begin{equation}
\label{satellite-b2}
C_{4}(z)=\frac{2.88z^2 - 4.896z + 2.074}{1.0z^2 - 0.42z - 0.3465 - 0.03915}. \nonumber
\end{equation} 
%
\begin{equation}
\label{satellite-c2}
C_{5}(z)=\frac{0.43z^2 - 0.2408z - 0.1316}{1.0z^2 + 1.5z + 0.97 + 0.183}. \nonumber
\end{equation}

All experiments were conducted on an otherwise idle Intel Core i$7$-$4790$ 
CPU $3$.$60$ GHz, $16$ GB of RAM, and Linux OS.  All times given are wall 
clock time in seconds as measured by the UNIX time command.

@@

\caption{Experimental results. \label{tab:results}}
\end{table}
\pksay{TODO: @Lucas: Please complete $G_x$ in table.}
%---------------------------------

>>>>

%Two proportional-integral (PI) controllers are designed by Wang {\it et al.} 
%for the cruise control plant $G(z)$~\cite{DBLP:conf/hybrid/WangGRJF16}, 
%which has the following mathematical model
%
%\begin{equation}
%\label{cruise-control-g1}
%C_{1}(z)=\frac{1.51z-1.3586}{z-1}, \nonumber
%\end{equation} 
%
%\begin{equation}
%\label{cruise-control-g2}
%C_{2}(z)=\frac{2.72z^2 - 4.153z + 1.896}{1.0z^2 - 1.844z + 0.8496}. \nonumber
%\end{equation}

The second set of benchmarks considers a simple spring-mass 
damper~\cite{DBLP:conf/hybrid/WangGRJF16}, where the discrete 
plant dynamics is represented by the following z-expression
%
%where both discrete 
%plant dynamics and controller are represented by the following 
%z-expression, resp.
%
\begin{equation}
\label{spring-mass-damper-g}
G_2(z)=\frac{5\times{10^{-5}}z + 5\times{10^{-5}}}{z^2 - 2z + 1.0001}. \nonumber
\end{equation} 
%
%\begin{equation}
%\label{spring-mass-damper-c}
%C_3(z)=\frac{1.28\times{10^{3}}z^2 - 1.354240\times{10^{3}}z + 0.074879\times{10^{3}}}{z^2 - 1.4990z + 0.4995}. \nonumber
%\end{equation}

A third set of benchmarks that consists of a physical plant for satellite
applications is considered~\cite{Franklin15}, in order to evaluate the
present approach full capabilities.  In particular, satellites often require
attitude (pose) control for proper orientation of antennas and sensors
w.r.t.  earth.  The satellite attitude control is typically used for
three-axis attitude tracking, but here only one axis at a time is
considered.  The motion equation for the one-axis system, despising
disturbance torques, is given by
%
\begin{equation}
\label{eq:satelliteode}
I\cdot \ddot{\theta} = \tau_{C},
\end{equation}

\noindent where $I$ is the inertia moment of satellite about its mass center, $\tau_{C}$ is the control 
torque applied by thusters, and $\theta$ is the controlled attitude angle. 
Normalizing Eq.~\eqref{eq:satelliteode} by defining the control signal $u=\frac{\tau_{C}}{I}$ and 
taking Laplace transform, the following $s$-domain transfer function $G(s)$ is obtained
%
\begin{equation}
\label{eq:satellitetf}
G_{3}(s)=\frac{\theta(s)}{u(s)}=\frac{1}{s^2},
\end{equation}

\noindent using the ZOH discretisation defined in Eq.~\eqref{eq:pulsetf}, 
the following $z$-domain model is obtained
%
\begin{equation}
G_{3}(z)= \frac{T^{2}}{2} \frac{z+1}{(z+1)^{2}}.
\end{equation}

%The discrete controllers $C_{4}$ and $C_{5}$ for the satellite plant $G_{3}$, discretized with sample time $1s$ and $2s$ respectively, 
%are represented by the following z-expression:
%
%\begin{equation}
%\label{satellite-b2}
%C_{4}(z)=\frac{2.88z^2 - 4.896z + 2.074}{1.0z^2 - 0.42z - 0.3465 - 0.03915}. \nonumber
%\end{equation} 
%
%\begin{equation}
%\label{satellite-c2}
%C_{5}(z)=\frac{0.43z^2 - 0.2408z - 0.1316}{1.0z^2 + 1.5z + 0.97 + 0.183}. \nonumber
%\end{equation}

The fourth (and last) set of benchmarks considers the following description for the plant 
$G_{4}(s)$, which is typically used for evaluating stability margins~\cite{bhattacharyya97,keel_Bhattacharyya_examples}
%
\begin{equation}
\label{exampleA}
G_{4}(s)=\frac{s-1}{s^{2}-s-2}
\end{equation}
%
\noindent where $G_{4}(z)$ is obtained using the ZOH discretisation defined 
in Eq.~\eqref{eq:pulsetf} with $3$ different sample times ($0.1$, $0.05$, and $0.03$ 
seconds).

\textcolor{red}{Pascal: Can you please check whether this configuration is correct?}
All experiments were conducted on an otherwise idle Intel Core i$7$-$4790$ 
CPU $3$.$60$ GHz, $16$ GB of RAM, and Linux OS.  All times given are wall 
clock time in seconds as measured by the UNIX time command.

@@

\caption{Experimental results. \label{tab:results}}
\end{table}
%---------------------------------
